---
title: "Homework week 1 part b"
author: "Lisa Crone"
date: "10/4/2021"
output:
  html_document: default
  pdf_document: default
---
Task: _Create an HTML document that samples 100 values from a log-normal distribution (say, mu=1, sigma=.25); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in the text._

### 1. A lognormal dataset

```{r}
samples = 100
mean = 1
sd = 0.25
data <- rlnorm(samples,meanlog = mean,sdlog = sd)
```

### 2. Histogram
**a)**
A histogram of dataset "data" with titles
```{r}
bins = 15

hist(data, breaks = bins, main = "Histogram of data",xlab = "numbers",ylab = "frequency")
```

**b)**
logarithmic histogram
```{r}
hist(log(data), breaks = bins, main = "Logarithmic histogram of data",xlab = "numbers",ylab = "frequency")
```

### 3.Mean and variance
```{r}
mean(data)
var(data)
```
The mean of the data set is **`r mean(data)`** and the variance **`r var(data)`** 
